---
title: "World_Bank"
output: html_document
date: "2024-04-04"
---


For the 2009 data
```{r}
library(haven)
data <- read_dta("/Users/homedepotsoup/Desktop/Econo2/IND_2009_EUS_V01_M_V06_A_GLD_ALL.dta")
```

The code below counts how many of each code there are and creates a dataframe.
```{r}
counts <- table(data$industrycat_isic_year)

count_df <- as.data.frame(counts)
colnames(count_df)[1] <- "ISIC"
# min, median, max, and quartiles of frequencies of job codes appearing
summary(count_df$Freq)
```

Below is a function that groups job codes into their corresponding ISIC 3.1 division, i.e codes that start with 01 or 02 are in the agriculture, hunting, and forestry division. Then it creates a table that sums the frequencies of each category appearing. 
```{r}
categorize_code <- function(code) {
  if(is.na(code) || code == "") {
    return("Unemployed")
  }
  
  first_two_digits <- as.numeric(substr(code, 1, 2))
  
  # Categorization logic based on the first two digits
  if(first_two_digits == 1 || first_two_digits == 2) {
    return("Agriculture, hunting and forestry")
  } else if(first_two_digits == 5) {
    return("Fishing")
  } else if(first_two_digits >= 10 && first_two_digits <= 14) {
    return("Mining and quarrying")
  } else if(first_two_digits >= 15 && first_two_digits <= 37) {
    return("Manufacturing")
  } else if(first_two_digits == 40 || first_two_digits == 41) {
    return("Electricity, gas and water supply")
  } else if(first_two_digits == 45) {
    return("Construction")
  } else if(first_two_digits >= 50 && first_two_digits <= 52) {
    return("Wholesale and retail trade")
  } else if(first_two_digits == 55) {
    return("Hotels and restaurants")
  } else if(first_two_digits >= 60 && first_two_digits <= 64) {
    return("Transport, storage and communications")
  } else if(first_two_digits >= 65 && first_two_digits <= 67) {
    return("Financial intermediation")
  } else if(first_two_digits >= 70 && first_two_digits <= 74) {
    return("Real estate, renting and business activities")
  } else if(first_two_digits == 75) {
    return("Public administration and defence")
  } else if(first_two_digits == 80) {
    return("Education")
  } else if(first_two_digits == 85) {
    return("Health and social work")
  } else if(first_two_digits >= 90 && first_two_digits <= 93) {
    return("Other community, social and personal service activities")
  } else if(first_two_digits >= 95 && first_two_digits <= 97) {
    return("Activities of private households")
  } else if(first_two_digits == 99) {
    return("Extraterritorial organizations and bodies")
  } else {
    return("Unemployed")
  }
}

count_df$ISIC <- as.character(count_df$ISIC)

count_df$Category <- sapply(count_df$ISIC, categorize_code)

category_counts <- table(count_df$Category)
category_counts_df <- as.data.frame(category_counts)
names(category_counts_df) <- c("Category", "Count")


category_counts_df$Category <- as.factor(category_counts_df$Category)

# Use the aggregate function to sum frequencies for each category
summed_freqs <- aggregate(Freq ~ Category, data = count_df, FUN = sum)

print(summed_freqs)
```

Location is urban if 1 and rural is 0
```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

count_df <- data.frame(ISIC = data$industrycat_isic_year, Urban = data$urban, Category = data$Category)

Urban_in_category <- aggregate(Urban ~ Category, data = count_df, FUN = sum)

print(Urban_in_category)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Urban_proportion_in_category <- aggregate(Urban ~ Category, data = count_df, FUN = calculate_proportion)

summed_freqs$urban <- Urban_proportion_in_category$Urban

print(Urban_proportion_in_category)

```

Calculate the number of males
```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

count_df <- data.frame(ISIC = data$industrycat_isic_year, Male = data$male, Category = data$Category)

males_in_category <- aggregate(Male ~ Category, data = count_df, FUN = sum)

print(males_in_category)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Male_proportion_in_category <- aggregate(Male ~ Category, data = count_df, FUN = calculate_proportion)

summed_freqs$males <- Male_proportion_in_category$Male

print(Male_proportion_in_category)

```

Literacy where 1 is can read and write and 0 is cannot 

```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

count_df <- data.frame(ISIC = data$industrycat_isic_year, Literacy = data$literacy, Category = data$Category)

Literacy_in_category <- aggregate(Literacy ~ Category, data = count_df, FUN = sum)

print(Literacy_in_category)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Literacy_proportion_in_category <- aggregate(Literacy ~ Category, data = count_df, FUN = calculate_proportion)

summed_freqs$literacy <- Literacy_proportion_in_category$Literacy

print(Literacy_proportion_in_category)
```

Calculate the average age
```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

age_df <- data.frame(ISIC = data$industrycat_isic_year, Age = data$age, Category = data$Category)

average_age_in_category <- aggregate(Age ~ Category, data = age_df, FUN = mean, na.rm = TRUE)

summed_freqs$avg_age <- average_age_in_category$Age

print(average_age_in_category)

```

Get the average household size
```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

hsize_df <- data.frame(ISIC = data$industrycat_isic_year, HSize = data$hsize, Category = data$Category)

average_hsize_in_category <- aggregate(HSize ~ Category, data = hsize_df, FUN = mean, na.rm = TRUE)

summed_freqs$avg_hsize <- average_hsize_in_category$HSize

print(average_hsize_in_category)

```

School 1 is attended and 0 it not
```{r}
data$Category <- sapply(as.character(data$industrycat_isic_year), categorize_code)

count_df <- data.frame(ISIC = data$industrycat_isic_year, School = data$school, Category = data$Category)

School_in_category <- aggregate(School ~ Category, data = count_df, FUN = sum)

print(School_in_category)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

School_proportion_in_category <- aggregate(School ~ Category, data = count_df, FUN = calculate_proportion)

newrow <- data.frame(Category = "Extraterritorial organizations and bodies", School=0)
r <- 5
School_proportion_in_category <- rbind(School_proportion_in_category[1:r, ], newrow, School_proportion_in_category[-(1:r),])

print(School_proportion_in_category)


summed_freqs$school <- School_proportion_in_category$School

print(School_proportion_in_category)

```

Marital Status
```{r}
# Check labels for what the values of marital mean.
unique(data$marital)
```


```{r}
marital_counts <- data %>%
  group_by(Category, marital) %>%
  summarise(count = n(), .groups = 'drop')
print(marital_counts)

marital_summary <- marital_counts %>%
  group_by(Category) %>%
  summarise(marital_vector = list(setNames(count, marital)), .groups = 'drop')

summed_freqs <- summed_freqs %>%
  left_join(marital_summary, by = "Category")
```


labor status
```{r}
# check label for what the values of lstatus mean
unique(data$lstatus)
```


```{r}
labor_counts <- data %>%
  group_by(Category, lstatus) %>%
  summarise(count = n(), .groups = 'drop')
print(marital_counts)

labor_summary <- labor_counts %>%
  group_by(Category) %>%
  summarise(labor_vector = list(setNames(count, lstatus)), .groups = 'drop')

summed_freqs <- summed_freqs %>%
  left_join(labor_summary, by = "Category")
```


Vocational status
```{r}
count_df <- data.frame(ISIC = data$industrycat_isic_year, vocation = data$vocational, Category = data$Category)

vocation_in_category <- aggregate(vocation ~ Category, data = count_df, FUN = sum)

vocation_proportion_in_category <- aggregate(vocation ~ Category, data = count_df, FUN = calculate_proportion)

summed_freqs$vocation <- vocation_proportion_in_category$vocation


print(vocation_proportion_in_category)
```