

```{r}
data2 <- read_dta("IND_2011_EUS_V01_M_V06_A_GLD_ALL.dta")
```

Counts how many of each code there is, makes a table
```{r}
counts2 <- table(data2$industrycat_isic_year)

count_df2 <- as.data.frame(counts2)
colnames(count_df2)[1] <- "ISIC"
summary(count_df2$Freq)
```

Uses ISIC 4, so the categorization is different. Process is the same. 
```{r}
categorize_code2 <- function(code) {
  if(is.na(code) || code == "") {
    return("Unemployed")
  }
  
  first_two_digits <- as.numeric(substr(code, 1, 2))
  
  if(first_two_digits >= 1 && first_two_digits <= 3) {
    return("Agriculture, forestry, and fishing")
  } else if(first_two_digits >= 5 && first_two_digits <= 9) {
    return("Mining and Quarrying")
  } else if(first_two_digits >= 10 && first_two_digits <= 33) {
    return("Manufacturing")
  } else if(first_two_digits == 35) {
    return("Electricity, gas, steam and air conditioning supply")
  } else if(first_two_digits >= 36 && first_two_digits <= 39) {
    return("Water supply; sewerage, waste management and remediation activities")
  } else if(first_two_digits >= 41 && first_two_digits <= 43) {
    return("Construction")
  } else if(first_two_digits >= 45 && first_two_digits <= 47) {
    return("Wholesale and retail trade; repair of motor vehicles and motorcycles")
  } else if(first_two_digits >= 49 && first_two_digits <= 53) {
    return("Transportation and storage")
  } else if(first_two_digits >= 55 && first_two_digits <= 56) {
    return("Accommodation and food service activities")
  } else if(first_two_digits >= 58 && first_two_digits <= 63) {
    return("Information and communication")
  } else if(first_two_digits >= 64 && first_two_digits <= 66) {
    return("Financial and insurance activities")
  } else if(first_two_digits == 68) {
    return("Real estate activities")
  } else if(first_two_digits >= 69 && first_two_digits <= 75) {
    return("Professional, scientific, and technical activities")
  } else if(first_two_digits >= 77 && first_two_digits <= 82) {
    return("Administrative and support service activities")
  } else if(first_two_digits == 84) {
    return("Public administration and defence; compulsory social security")
  } else if(first_two_digits == 85) {
    return("Education")
  } else if(first_two_digits >= 86 && first_two_digits <= 88) {
    return("Human health and social work activities")
  } else if(first_two_digits >= 90 && first_two_digits <= 93) {
    return("Arts, entertainment and recreation")
  } else if(first_two_digits >= 94 && first_two_digits <= 96) {
    return("Other service activities")
  } else if(first_two_digits >= 97 && first_two_digits <= 98) {
    return("Activities of households as employers; undifferentiated goods- and services-producing activities of households for own use")
  } else if(first_two_digits == 99) {
    return("Activities of extraterritorial organizations and bodies")
  } else {
    return("Unemployed")
  }
}

count_df2$ISIC <- as.character(count_df2$ISIC)

count_df2$Category <- sapply(count_df2$ISIC, categorize_code2)

category_counts2 <- table(count_df2$Category)
category_counts_df2 <- as.data.frame(category_counts2)
names(category_counts_df2) <- c("Category", "Count")


category_counts_df2$Category <- as.factor(category_counts_df2$Category)

summed_freqs2 <- aggregate(Freq ~ Category, data = count_df2, FUN = sum)


print(summed_freqs2)

```

Location is urban if 1 and rural is 0
```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, Urban = data2$urban, Category = data2$Category)

Urban_in_category2 <- aggregate(Urban ~ Category, data = count_df2, FUN = sum)

print(Urban_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Urban_proportion_in_category2 <- aggregate(Urban ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$urban <- Urban_proportion_in_category2$Urban



print(Urban_proportion_in_category2)

```

Calculate the number of males
```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, Male = data2$male, Category = data2$Category)

males_in_category2 <- aggregate(Male ~ Category, data = count_df2, FUN = sum)

print(males_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Male_proportion_in_category2 <- aggregate(Male ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$males <- Male_proportion_in_category2$Male


print(Male_proportion_in_category2)
```

Literacy where 1 can read and write and 0 is cannot 

```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, Literacy = data2$literacy, Category = data2$Category)

Literacy_in_category2 <- aggregate(Literacy ~ Category, data = count_df2, FUN = sum)

print(Literacy_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Literacy_proportion_in_category2 <- aggregate(Literacy ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$literacy <- Literacy_proportion_in_category2$Literacy


print(Literacy_proportion_in_category2)
```

Calculate the average age
```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

age_df2 <- data.frame(ISIC = data2$industrycat_isic_year, Age = data2$age, Category = data2$Category)

average_age_in_category2 <- aggregate(Age ~ Category, data = age_df2, FUN = mean, na.rm = TRUE)

summed_freqs2$avg_age <- average_age_in_category2$Age


print(average_age_in_category2)

```

Calculate average household size
```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

hsize_df2 <- data.frame(ISIC = data2$industrycat_isic_year, HSize = data2$hsize, Category = data2$Category)

average_hsize_in_category2 <- aggregate(HSize ~ Category, data = hsize_df2, FUN = mean, na.rm = TRUE)

summed_freqs2$avg_hsize <- average_hsize_in_category2$HSize


print(average_hsize_in_category2)
```

School 1 is attended and 0 it not
```{r}
data2$Category <- sapply(as.character(data2$industrycat_isic_year), categorize_code2)

count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, School = data2$school, Category = data2$Category)

School_in_category2 <- aggregate(School ~ Category, data = count_df2, FUN = sum)

print(School_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

School_proportion_in_category2 <- aggregate(School ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$school <- School_proportion_in_category2$School

print(School_proportion_in_category2)
```
Marital Status
```{r}
# Check labels for what the values of marital mean.
unique(data2$marital)

data2 <- as.data.frame(data2, stringsAsFactors = FALSE)

data2$marital2 <- ifelse(is.na(data2$marital), NA, 
                         ifelse(data2$marital == 1, 1, 0))
```

```{r}
count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, Marital = data2$marital2, Category = data2$Category)

marital_in_category2 <- aggregate(Marital ~ Category, data = count_df2, FUN = sum)

print(marital_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

Marital_proportion_in_category2 <- aggregate(Marital ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$marital <- Marital_proportion_in_category2$Marital

print(Marital_proportion_in_category2)
```
labor status
```{r}
# check label for what the values of lstatus mean
unique(data2$lstatus)

data2$labor <- ifelse(is.na(data2$lstatus), NA, 
                         ifelse(data2$lstatus == 1, 1, 0))

```

```{r}
count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, labor = data2$labor, Category = data2$Category)

labor_in_category2 <- aggregate(labor ~ Category, data = count_df2, FUN = sum)

print(labor_in_category2)

calculate_proportion <- function(x) {
  sum(x) / length(x)
}

labor_proportion_in_category2 <- aggregate(labor ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$labor <- labor_proportion_in_category2$labor

print(labor_proportion_in_category2)
```

Vocational status
```{r}
count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, vocation = data2$vocational, Category = data2$Category)

vocation_in_category2 <- aggregate(vocation ~ Category, data = count_df2, FUN = sum)

vocation_proportion_in_category2 <- aggregate(vocation ~ Category, data = count_df2, FUN = calculate_proportion)

summed_freqs2$vocation <- vocation_proportion_in_category2$vocation


print(vocation_proportion_in_category2)
```
Average wages
```{r}
count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, wages = data2$wage_no_compen, Category = data2$Category)

wages_in_category2 <- aggregate(wages ~ Category, data = count_df2, FUN = sum)

wages_proportion_in_category2 <- aggregate(wages ~ Category, data = count_df2, FUN = mean, na.rm = TRUE)

summed_freqs2$avg_wages <- wages_proportion_in_category2$wages


print(wages_proportion_in_category2)
```
Average hours worked
```{r}
count_df2 <- data.frame(ISIC = data2$industrycat_isic_year, hours = data2$whours, Category = data2$Category)

hours_in_category2 <- aggregate(hours ~ Category, data = count_df2, FUN = sum)

hours_proportion_in_category2 <- aggregate(hours ~ Category, data = count_df2, FUN = mean, na.rm = TRUE)

summed_freqs2$avg_hours <- hours_proportion_in_category2$hours


print(hours_proportion_in_category2)
```





Below drops the union territories from the dataframe, as they're small enough that they won't impact our calculations so much. Based on this website here: https://knowindia.india.gov.in/states-uts/
Note: probably going to look at population/union territory size and revise which ones to drop. 
```{r}

data_filtered2 <- data2 %>%
  filter(!is.na(industrycat_isic_year) & industrycat_isic_year != "")


names_to_drop <- c(
  "35  - Andaman & Nicobar Islands",
  "4 - Chandigarh",
  "26 - Dadra & Nagar Haveli",
  "7 - Delhi",
  "1 - Jammu & Kashmir",
  "31 - Lakshadweep",
  "34 - Pondicheri"
)


frequency_table2 <- table(data_filtered2$subnatid1)

sorted_frequencies2 <- sort(frequency_table2)


for (name in names(sorted_frequencies2)) {  # Iterate over unique names
  count <- frequency_table2[name]  # Get the count for each unique name
  print(paste("Number of", name, ":", count))  # Print the name and its count
}

territories2 <- as.data.frame(frequency_table2)

```



```{r}
names_to_drop <- c(
  "35  - Andaman & Nicobar Islands",
  "4 - Chandigarh",
  "26 - Dadra & Nagar Haveli",
  "7 - Delhi",
  "1 - Jammu & Kashmir",
  "31 - Lakshadweep",
  "34 - Pondicheri"
)

df_filtered <- data2 %>%
  filter(!data2$subnatid1 %in% names_to_drop)  # Filter out rows where 'name' matches 'names_to_drop'

print(unique(df_filtered$subnatid1))

```



To replicate this, download the india_state_boundary .shp, .dbf, and .shx files from https://github.com/AnujTiwari/India-State-and-Country-Shapefile-Updated-Jan-2020
```{r}
library(stringr)

library(ggplot2)
library(sf)
library(stringdist)


india_shapefile <- st_read("India_State_Boundary.shp")

territories2$subnatid1_clean <- gsub("^[0-9]+ - ", "", territories2$Var1)



india_shapefile$State_Name <- tolower(trimws(india_shapefile$State_Name))
territories2$subnatid1_clean <- tolower(trimws(territories2$subnatid1_clean))

correction_map <- list(
  "orissa" = "odisha",
  "chhattisgarh" = "chhattishgarh",
  "gujrat" = "gujarat",
  "maharastra" = "maharashtra",
  "tamil nadu" = "tamilnadu",
  "pondicheri" = "puducherry",
  "andaman & nicober" = "andaman & nicobar",
  "uttaranchal" = "uttarakhand",
  "jammu & kashmir" = "jammu and kashmir"
)

mutation2 <- territories2 %>%
  mutate(State_Name = sapply(subnatid1_clean, function(x) {
    if (x %in% names(correction_map)) {
      return(correction_map[[x]])
    } else {
      return(x)  
    }
  }))
daman_and_dadra_sum <- mutation2 %>%
  filter(State_Name %in% c("daman & diu", "dadra & nagar haveli")) %>%
  summarise(
    State_Name = "daman and diu and dadra and nagar haveli",
    Freq = sum(Freq)
  )

# Append the new row to the original data frame
mutation2 <- bind_rows(mutation2, daman_and_dadra_sum) 
```

Of some note, Ladakh was part of Jammu and Kashmir until 2019 when it became a separate territory, so the data from Jammu and Kashmir is spread among Ladakh as well. 
Similarly, Telengana didn't become a state until 2014. Until that time, it had been a part of Andhra Pradesh.
```{r}
merged_data <- merge(india_shapefile, mutation2, by = "State_Name",all.x=TRUE)

# Plot the merged data
ggplot(data = merged_data) +
  geom_sf(aes(fill = Freq), color = "black", lwd = 0.5) + 
  geom_sf_text(aes(label = State_Name), color="red", size = 2, check_overlap = FALSE) +  # Add state name labels
  theme_minimal() +
  labs(
    title = "Map of India with number of observations in each state or union territory",
    fill = "number of observations"
  )
# Unfortunately, sizing the labels as they are mean some of them have been cut off and cannot be seen. You can adjust the size of the label, but break out the reading glasses if you do. 
```

```{r}
dominant_category2 <- data_filtered2 %>%
   group_by(subnatid1, Category) %>%
   tally() %>%
   group_by(subnatid1) %>%
   filter(n == max(n)) %>%
   select(subnatid1, Category)



print(dominant_category2)


dominant_category2 <- data_filtered2 %>%
  group_by(subnatid1, Category) %>%
  tally() %>%
  group_by(subnatid1) %>%
  mutate(rank = dense_rank(desc(n))) %>%  # Add rank for each category within subnatid1
  filter(rank == 1 & Category != "Agriculture, forestry, and fishing" |  # Filter dominant category (excluding Agriculture)
         rank == 2) %>%                                         # OR keep the second largest category if dominant is Agriculture
  select(subnatid1, Category)

print(dominant_category2)


```

```{r}

dominant_category2$subnatid1_clean <- gsub("^[0-9]+ - ", "", dominant_category2$subnatid1)

dominant_category2$subnatid1_clean <- tolower(trimws(dominant_category2$subnatid1_clean))

mutate_category2 <- dominant_category2 %>%
  mutate(State_Name = sapply(subnatid1_clean, function(x) {
    if (x %in% names(correction_map)) {
      return(correction_map[[x]])
    } else {
      return(x)  
    }
  }))



merged_categories2 <- merge(india_shapefile, mutate_category2, by = "State_Name",all.x=TRUE)

cols_to_replace <- 2:4


# making sure Ladahk maps t0 Andhra Pradesh and Telengana to Jammu and Kashmir
merged_categories2[21, cols_to_replace] <- merged_categories2[17, cols_to_replace]

merged_categories2[38, cols_to_replace] <- merged_categories2[2, cols_to_replace]


# Plot the merged data
p <- ggplot(merged_categories2) +
  geom_sf(aes(fill = Category)) +
  scale_fill_viridis_d(option = "plasma", name = "Dominant Category") +
  theme_minimal() +
  labs(title = "Dominant Job Category by State in India without agriculture",
       subtitle = "Based on ISIC job code data")

p <- p + theme(plot.background = element_rect(fill = "white"))

ggsave(filename = "dominant_categories_india_2011_sans_ag.png", plot = p, width = 10, height = 8)

p

```

```{r}
library(xtable)
xt2 <- xtable(summed_freqs2)

print(xt2, floating = FALSE, tabular.environment = "tabular", include.rownames = FALSE, file = "table.tex")

# Wrap the LaTeX code in the landscape environment
cat("\\begin{landscape}\n", file = "table.tex", append = TRUE)
print(xt2, file = "table.tex", append = TRUE)
cat("\\end{landscape}\n", file = "table.tex", append = TRUE)
```



